**The status of the microbial census: an update**

### 2016-01-22 doc/notebook/Archaeal_data_acquisition.Rmd
Harvest EMIRGE data that was deposited into GenBank

write.table(spread_sheet_good[,colnames(metadata_good)], file="data/mothur/archaea.good.metadata", quote=TRUE, sep="\t", col.names=F, append=T)

#we'll output the sequence names so the sequences aren't included in the
#rarefaction analysis
write(rownames(spread_sheet_good), file="data/mothur/archaea.sc_emirge.accnos")
```

@@

write.table(archaea_emirge_metadata, file="data/mothur/archaea.good.metadata", quote=TRUE, sep="\t", col.names=F, append=T)

#we'll output the sequence names so the sequences aren't included in the
#rarefaction analysis
write(rownames(archaea_emirge_metadata), file="data/mothur/archaea.sc_emirge.accnos", append=T)
```

>>>>

write.table(spread_sheet_good[,colnames(metadata_good)], file="data/mothur/archaea.good.metadata", quote=TRUE, sep="\t", col.names=F, append=T)
```

@@

write.table(archaea_emirge_metadata, file="data/mothur/archaea.good.metadata", quote=TRUE, sep="\t", col.names=F, append=T)
```

### 2016-01-22 doc/notebook/Bacterial_data_acquisition.Rmd
Harvest EMIRGE data that was deposited into GenBank

write.table(spread_sheet_good[,colnames(metadata_good)], file="data/mothur/bacteria.good.metadata", quote=TRUE, na="NA", sep="\t", col.names=F, append=T)

#we'll output the sequence names so the sequences aren't included in the
#rarefaction analysis
write(rownames(spread_sheet_good), file="data/mothur/bacteria.sc_emirge.accnos")
```

@@

write.table(bacteria_emirge_metadata, file="data/mothur/bacteria.good.metadata", quote=TRUE, sep="\t", col.names=F, append=T)

#we'll output the sequence names so the sequences aren't included in the
#rarefaction analysis
write(rownames(bacteria_emirge_metadata), file="data/mothur/bacteria.sc_emirge.accnos", append=T)
```

>>>>

write.table(spread_sheet_good[,colnames(metadata_good)], file="data/mothur/bacteria.good.metadata", quote=TRUE, na="NA", sep="\t", col.names=F, append=T)
```

@@

write.table(bacteria_emirge_metadata, file="data/mothur/bacteria.good.metadata", quote=TRUE, sep="\t", col.names=F, append=T)
```
